### 2014-02-22 paper/retrofit.tex
no definition for T yet

iTE  ::=  iTE, lconf id il tS ie, ldots

@@

\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iconf iS (iniTE (lconf id il tS (iniE ie)))
.->
iconf iS' (iniTE (lconf id il' tS (iniE ie')))
|}

\and
\inferrule[I-step]
{|
conf tS (te) -> conf tS' te'
|}
{|
iconf iS (iniTE (lconf id il tS (IT te)))
.->
iconf iS (iniTE (lconf id il tS' (IT te')))
|}

@@

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|\\
|fresh (id')|
}
{|
iconf iS (lconf id il tS (fork ie), ldots)
.->
iconf iS' (lconf id il tS id', ldots, lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}

>>>>

@@

\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iS ,(iniTE (lconf id il tS (iniE ie)))
.-.>
iS', (iniTE (lconf id il' tS (iniE ie')))
|}

\and
\inferrule[I-step]
{|
conf tS (te) -> conf tS' te'
|}
{|
iS, (iniTE (lconf id il tS (IT te)))
.-.>
iS, (iniTE (lconf id il tS' (IT te')))
|}

@@

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|\\
|fresh (id')|\\
|iTE' THole = iniTE (lconf id il tS id'), THole|
}
{|
iS, iniTE (lconf id il tS (fork ie))
.-.>
iS', iniTE' (lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}
